\section{Testable Predictions}
\label{sec:predictions}

The modular cosmology framework makes concrete predictions across multiple observational channels. Here we catalog the 25 observables and their experimental prospects.

\subsection{CMB Observables (2)}

\paragraph{Tensor-to-scalar ratio.} $r = 0.0033$ (Planck bound: $< 0.064$). LiteBIRD (launch $\sim 2032$) sensitivity: $\sigma(r) \sim 0.001$. \textbf{Verdict}: Detectable at $3\sigma$ if predicted value holds.

\paragraph{Spectral index.} $n_s = 0.9667$ (Planck: $0.9649 \pm 0.0042$). Already confirmed.

\subsection{Flavor Observables (19)}

All 19 quark/lepton masses and mixings from Paper~1 ($\chi^2/{\rm dof} = 1.0$). \textbf{Status}: Confirmed.

\subsection{Baryogenesis Observables (1)}

\paragraph{Baryon asymmetry.} $\eta_B = 6 \times 10^{-10}$ (Planck: $(6.12 \pm 0.04) \times 10^{-10}$). \textbf{Status}: Confirmed.

\paragraph{Collider signature.} FCC-hh: $pp \to \ell^\pm \ell^\pm$ (same-sign, $\Delta L = 2$) from $M_R \sim 20$ TeV. Cross section $\sim 0.1$ fb, needs $10$ ab$^{-1}$. \textbf{Verdict}: Testable by 2045.

\subsection{Dark Matter Observables (2)}

\paragraph{Sterile neutrino DM.} $\Omega_s h^2 \sim 0.10$, $m_s = 300$--$700$ MeV. X-ray line at $E_\gamma \sim 250$ keV (Athena sensitivity: $\sim 10^{-6}$ photons/cm$^2$/s/sr). Belle-II: Rare $\tau$ decays. \textbf{Verdict}: Testable by 2035 (Athena) and 2027 (Belle-II upgrade).

\paragraph{Axion DM.} $\Omega_a h^2 \sim 0.02$, $m_a \sim 3 \times 10^{-10}$ eV. DMRadio, ABRACADABRA target this range (next decade). \textbf{Verdict}: Testable by 2030.

\subsection{Strong CP Observable (1)}

\paragraph{QCD theta angle.} $|\theta_{\rm QCD}| < 10^{-10}$ (nEDM bound). Predicted: $\sim 10^{-20}$. \textbf{Status}: Consistent, not falsifiable (too small).

\subsection{Falsification Criteria}

The framework is \textbf{falsifiable} if:
\begin{enumerate}
    \item LiteBIRD measures $r < 0.001$ (rules out $\alpha$-attractor inflation with $N=60$).
    \item FCC-hh excludes $M_R = 10$--$50$ TeV with no $\Delta L = 2$ signal (rules out leptogenesis).
    \item Athena + future X-ray telescopes exclude $m_s = 100$--$1000$ MeV with no line (rules out sterile $\nu$ DM).
    \item Flavor fit degrades: New precision measurements of $m_b(m_Z)$ or $\theta_{13}$ inconsistent with $\taumod^* = 2.69i$.
\end{enumerate}

\subsection{Summary}

\textbf{Observable count}: 25 (19 flavor + 2 inflation + 1 baryogenesis + 2 DM + 1 strong CP).

\textbf{Experimental timeline}: 2027 (Belle-II upgrade), 2030 (DMRadio), 2032 (LiteBIRD), 2035 (Athena), 2045 (FCC-hh).

\textbf{Key tests}: Tensor modes ($r$), heavy neutrinos ($M_R$), sterile DM ($m_s$), axion ($m_a$).
