\section{Complete Cosmological Timeline}
\label{sec:timeline}

Having established the individual cosmological mechanisms (Sections~\ref{sec:inflation}--\ref{sec:strongcp}), we now synthesize them into a complete timeline of the universe from $t \sim 10^{-35}$ s to the present. This section traces the sequence of modulus-driven events that shape the thermal and matter content of the cosmos.

\subsection{Phase I: Inflation ($t = 10^{-35}$--$10^{-33}$ s)}

\textbf{Dominant modulus}: $\sigmamod$ (blow-up mode)

The universe begins in an inflationary phase driven by the $\sigmamod$ modulus at $\langle \sigmamod \rangle \sim 27 M_{\text{Pl}}$. The K\"ahler potential $K = -3 \log(\sigmamod + \bar{\sigmamod})$ induces $\alpha$-attractor inflation with $n_s = 0.9667$, $r = 0.0033$. After $N \approx 60$ e-folds, inflation ends and $\sigmamod$ oscillates.

\textbf{Key events}:
\begin{itemize}
    \item $t \sim 10^{-35}$ s: Inflation begins, $H_{\text{inf}} \sim 10^{14}$ GeV
    \item $t \sim 10^{-33}$ s: Inflation ends, $\sigmamod$ oscillates
    \item PQ symmetry never restored: $f_a \sim 10^{16}$ GeV $> \TRH^{(1)}$
\end{itemize}

\subsection{Phase II: First Reheating ($t = 10^{-33}$--$10^{-32}$ s)}

\textbf{Process}: $\sigmamod$ decay

The inflaton decays into SM particles with $\TRH^{(1)} \sim 10^{13}$ GeV. Thermal bath established.

\subsection{Phase III: Modulus Stabilization ($t \sim 10^{-30}$ s)}

\textbf{Process}: $\taumod$ modulus stabilizes at $\taumod^* = 2.69i$

Yukawa couplings freeze: $Y_{ij}(\taumod^*) \Rightarrow$ all 19 flavor observables.

\subsection{Phase IV: Second Reheating ($t \sim 10^{-10}$ s)}

\textbf{Process}: $\taumod$ decay

Produces $N_R$ (heavy + light), $\TRH^{(2)} \sim 10^9$ GeV.

\subsection{Phase V: Leptogenesis ($t \sim 10^{-9}$ s)}

\textbf{Process}: $N_1, N_2$ CP-violating decays

Resonant enhancement yields $\eta_B \sim 6 \times 10^{-10}$.

\subsection{Phase VI: Sterile Neutrino Freeze-Out ($t \sim 10^{-6}$ s)}

\textbf{Process}: Light $N_s$ become non-relativistic

$\Omega_s h^2 \sim 0.10$ (83\% of DM).

\subsection{Phase VII: Axion Oscillations ($t \sim 1$ s)}

\textbf{Process}: Axion field begins oscillating

$\Omega_a h^2 \sim 0.02$ (17\% of DM).

\subsection{Phase VIII: Big Bang Nucleosynthesis ($t \sim 1$--$100$ s)}

Light elements form with $\eta_B = 6 \times 10^{-10}$.

\subsection{Phase IX--XI: Matter Domination to Today}

CMB ($t \sim 380{,}000$ yr), structure formation, galaxies.

\subsection{Timeline Summary}

\begin{table}[h!]
\centering
\begin{tabular}{llll}
\toprule
\textbf{Phase} & \textbf{Time} & \textbf{Temperature} & \textbf{Event} \\
\midrule
I & $10^{-35}$ s & $10^{14}$ GeV & Inflation ($\sigmamod$) \\
II & $10^{-32}$ s & $10^{13}$ GeV & First reheating \\
III & $10^{-30}$ s & $10^{12}$ GeV & $\taumod^* = 2.69i$ \\
IV & $10^{-10}$ s & $10^9$ GeV & Second reheating \\
V & $10^{-9}$ s & $10^8$ GeV & Leptogenesis \\
VI & $10^{-6}$ s & $1$ GeV & Sterile $\nu$ freeze-out \\
VII & $1$ s & $1$ MeV & Axion oscillations \\
VIII & $1$--$100$ s & MeV & BBN \\
IX & $50{,}000$ yr & $1$ eV & Matter-rad equality \\
X & $380{,}000$ yr & $0.3$ eV & Recombination \\
XI & today & $10^{-13}$ eV & Structure \\
\bottomrule
\end{tabular}
\caption{Timeline: three moduli drive inflation, flavor, DM, baryogenesis, strong CP.}
\label{tab:timeline}
\end{table}
