\section{Discussion}
\label{sec:discussion}

\subsection{Assumptions}

Our framework rests on several key assumptions:

\paragraph{Three-moduli structure.} We assign specific roles to $\sigmamod$ (inflation), $\taumod$ (flavor), $\rhomod$ (strong CP). This is motivated by string compactifications where different moduli control different geometric/coupling sectors, but the precise mapping depends on the Calabi-Yau geometry.

\paragraph{Non-interference.} We assume moduli decay sequentially without disrupting prior processes. This requires hierarchical decay rates: $\Gamma_\sigmamod > \Gamma_\taumod > \Gamma_\rhomod$, which depends on modulus masses and couplings.

\paragraph{Superpotential forms.} Inflation robustness relies on $W(\sigmamod)$ being dominated by low-order terms. Flavor structure depends on modular forms $Y_{ij} \sim \eta(\taumod)^w$.

\subsection{Robustness}

\paragraph{Leptogenesis.} Requires $\Delta M/M \sim 10^{-7}$ and BR $\sim 10\%$. Both have $\sim 10\times$ freedom, giving $\sim 100$ viable parameter combinations.

\paragraph{Axion DM.} Relic density $\Omega_a \propto \theta_i^2 (f_a)^{7/6}$. For $f_a = (1$--$5) \times 10^{16}$ GeV and $\theta_i = 0.005$--$0.02$, $\Omega_a = 0.01$--$0.04$ (acceptable).

\subsection{Comparisons}

\paragraph{Standard leptogenesis.} Requires $M_R \gtrsim 10^9$ GeV (Davidson-Ibarra bound). We achieve it at $M_R \sim 20$ TeV via resonance.

\paragraph{QCD axion.} Typically $f_a \sim 10^{9}$--$10^{12}$ GeV (ADMX range). Ours is $f_a \sim 10^{16}$ GeV (GUT scale), beyond current experiments but testable next decade.

\paragraph{Starobinsky $R^2$.} Equivalent to our $\sigmamod$ inflation when $\alpha = 1$.

\subsection{Landscape and Vacuum Selection}

\paragraph{Uniqueness of $\taumod^* = 2.69i$.} String landscape has $\sim 10^{500}$ vacua. How often does $\taumod$ stabilize at values giving correct flavor? Unknown. Anthropic selection may be required.

\subsection{What Is NOT Explained}

\begin{enumerate}
    \item Dark energy ($\Lambda \sim 10^{-120} M_{\rm Pl}^4$): Not addressed.
    \item Hierarchy problem ($m_H \ll M_{\rm Pl}$): Requires SUSY or other BSM.
    \item Neutrino masses absolute scale: Lightest $m_\nu$ unconstrained.
\end{enumerate}

\subsection{Summary}

The framework is robust to $\mathcal{O}(10)$ parameter variations, but requires specific modulus roles and decay hierarchies. Comparisons with standard cosmology show enhancement mechanisms (resonance, GUT-scale $f_a$) that enable solutions at lower scales. Open questions include vacuum selection and dark energy.
