\section{Conclusions}
\label{sec:conclusions}

We have presented a unified framework for cosmology from string moduli, addressing inflation, dark matter, baryogenesis, and the strong CP problem within a single geometric structure. The main results are:

\subsection{Main Achievement}

A complete cosmological history from $t \sim 10^{-35}$ s to today, driven by three moduli:
\begin{itemize}
    \item $\sigmamod$ (blow-up mode): Inflation with $n_s = 0.9667$, $r = 0.0033$ ($\alpha$-attractor, equivalent to Starobinsky).
    \item $\taumod$ (complex structure at $2.69i$): Flavor (19 observables, Paper~1), sterile neutrino DM ($\Omega_s \sim 0.10$), resonant leptogenesis ($\eta_B = 6 \times 10^{-10}$).
    \item $\rhomod$ (K\"ahler): Axion DM ($\Omega_a \sim 0.02$), strong CP solution ($|\theta_{\rm QCD}| < 10^{-10}$).
\end{itemize}

\subsection{Key Result: Inflation Derived}

\textbf{Inflation is no longer assumed}—it emerges naturally from the K\"ahler potential $K = -3 \log(\sigmamod + \bar{\sigmamod})$ of a blow-up mode stabilized at $\langle \sigmamod \rangle \sim 27 M_{\rm Pl}$. This represents a fundamental shift: cosmology follows from string geometry, not ad hoc scalar fields.

\subsection{Observable Count}

\textbf{25 observables} from a single structure:
\begin{itemize}
    \item 19 flavor (6 quark masses, 3 lepton masses, 4 CKM, 3 PMNS, 3 neutrino mass differences)
    \item 2 inflation ($n_s$, $r$)
    \item 1 baryogenesis ($\eta_B$)
    \item 2 dark matter ($\Omega_s$, $\Omega_a$)
    \item 1 strong CP ($\theta_{\rm QCD}$)
\end{itemize}

\subsection{Testability and Falsifiability}

\textbf{Five experiments} probe this framework in the next 20 years:
\begin{enumerate}
    \item LiteBIRD (2032): Detects or rules out $r = 0.003$.
    \item Belle-II (2027): Probes $m_s \sim 500$ MeV in rare $\tau$ decays.
    \item Athena (2035): X-ray line at $E_\gamma \sim 250$ keV.
    \item DMRadio (2030): Axion mass $m_a \sim 10^{-10}$ eV.
    \item FCC-hh (2045): Heavy neutrinos $M_R \sim 20$ TeV, $\Delta L = 2$.
\end{enumerate}

\textbf{Falsification}: If LiteBIRD finds $r < 0.001$, or FCC-hh excludes $M_R = 10$--$50$ TeV, or Athena sees no sterile neutrino line, the framework is \textbf{ruled out}.

\subsection{Future Directions}

\begin{enumerate}
    \item \textbf{Explicit compactification}: Construct a Calabi-Yau manifold where $\sigmamod$, $\taumod$, $\rhomod$ play these roles. Compute modulus masses and couplings from first principles.
    \item \textbf{Vacuum selection}: Why $\taumod^* = 2.69i$? Develop dynamical or anthropic arguments for this value among $\sim 10^{500}$ landscape vacua.
    \item \textbf{Dark energy}: Extend to include cosmological constant $\Lambda \sim 10^{-120} M_{\rm Pl}^4$ (not addressed here).
    \item \textbf{SUSY breaking}: If moduli masses $\sim 10^{9}$--$10^{13}$ GeV set SUSY scale, compute soft terms and test at colliders.
\end{enumerate}

\subsection{Outlook}

String cosmology is no longer a theoretical curiosity—it is \textbf{testable and falsifiable}. The next two decades will determine whether the universe's history is written in the geometry of extra dimensions.

\vspace{1cm}

\noindent\textbf{Companion Paper}: The flavor analysis ($\taumod^* = 2.69i$, 19 observables, 79 pages) is presented in Ref.~\cite{Heitfeld:2025flavor} and is ready for expert review (Jan 2025).
