\section{Testable Predictions and Falsifiability}
\label{sec:predictions}

Unlike many beyond-the-Standard-Model theories that accommodate existing data but make no falsifiable predictions, our framework derives concrete quantitative predictions for observables not yet measured. These predictions are genuine outputs of the topological structure, not fitted parameters. We identify three near-term experimental tests that will decisively confirm or rule out this framework by 2030.

\subsection{Neutrinoless Double-Beta Decay}

\subsubsection{Theoretical Prediction}

Neutrinoless double-beta decay ($0\nu\beta\beta$) is a hypothetical nuclear process:
\begin{equation}
    (Z, A) \to (Z+2, A) + 2e^-,
\end{equation}
which violates lepton number by two units and can only occur if neutrinos are Majorana particles. The decay rate is proportional to the effective Majorana mass:
\begin{equation}
    \vev{m_{\beta\beta}} = \left| \sum_{i=1}^3 U_{ei}^2 m_i \right|,
    \label{eq:mbb_definition}
\end{equation}
where $U$ is the PMNS matrix and $m_i$ are the neutrino mass eigenvalues.

Using our predicted neutrino masses ($m_1 = 1.2$ meV, $m_2 = 8.7$ meV, $m_3 = 50.1$ meV) and PMNS matrix elements from Section~\ref{sec:results}, we compute:
\begin{equation}
    \vev{m_{\beta\beta}} = 10.5 \text{ meV}.
    \label{eq:mbb_prediction}
\end{equation}

\paragraph{Uncertainty estimate.}
The dominant uncertainties arise from:
\begin{enumerate}
    \item \textbf{Moduli stabilization:} $3.5\%$ systematic from KKLT (Appendix~\ref{app:kklt}) propagates to $\Delta m_{\beta\beta} \approx 0.4$ meV.
    
    \item \textbf{PMNS angles:} Experimental uncertainties on $\theta_{12}$, $\theta_{13}$ contribute $\sim 0.3$ meV via the $U_{ei}^2$ factors in Eq.~\eqref{eq:mbb_definition}.
    
    \item \textbf{Neutrino mass ordering:} We assume normal ordering (NO). If nature chooses inverted ordering (IO), our prediction is excluded. Current global fits favor NO at $2.5\sigma$ \cite{Esteban:2020cvm}.
    
    \item \textbf{Majorana phases:} The PMNS matrix contains two Majorana phases $\alpha_{21}$ and $\alpha_{31}$ that affect $\vev{m_{\beta\beta}}$. Our framework predicts:
    \begin{equation}
        \alpha_{21} = 112^\circ, \quad \alpha_{31} = 295^\circ.
    \end{equation}
    These arise from the complex phases in the seesaw mechanism (Section~\ref{sec:calculation}). Varying these within $\pm 20^\circ$ (conservative estimate) changes $\vev{m_{\beta\beta}}$ by $\sim 1.0$ meV.
\end{enumerate}

Combining in quadrature:
\begin{equation}
    \Delta m_{\beta\beta} = \sqrt{0.4^2 + 0.3^2 + 1.0^2} \approx 1.1 \text{ meV}.
\end{equation}

Thus our final prediction is:
\begin{equation}
    \boxed{\vev{m_{\beta\beta}} = (10.5 \pm 1.5) \text{ meV}}
    \label{eq:mbb_final}
\end{equation}

This range accounts for theoretical uncertainties while remaining precise enough to be falsifiable.

\subsubsection{Experimental Status and Timeline}

Current experimental limits on $\vev{m_{\beta\beta}}$ come from:
\begin{itemize}
    \item \textbf{KamLAND-Zen} (2022): $\vev{m_{\beta\beta}} < 36$--$156$ meV (90\% CL) \cite{KamLAND-Zen:2022tow}
    \item \textbf{GERDA} (2020): $\vev{m_{\beta\beta}} < 79$--$180$ meV (90\% CL) \cite{GERDA:2020xhi}
    \item \textbf{CUORE} (2022): $\vev{m_{\beta\beta}} < 75$--$350$ meV (90\% CL) \cite{CUORE:2022pcg}
\end{itemize}

The wide ranges reflect uncertainties in nuclear matrix elements for different isotopes ($^{136}$Xe, $^{76}$Ge, $^{130}$Te). Our prediction $10.5$ meV is well below current limits but will be probed by next-generation experiments:

\paragraph{LEGEND (Large Enriched Germanium Experiment for $0\nu\beta\beta$ Decay).}
LEGEND is a tonne-scale $^{76}$Ge detector with projected sensitivity \cite{LEGEND:2021bnm}:
\begin{equation}
    \vev{m_{\beta\beta}} > 9\text{--}24 \text{ meV at } 90\%\text{ CL (LEGEND-1000, 2027--2030)}.
\end{equation}
The range depends on nuclear matrix element calculations. Our prediction $10.5$ meV lies at the \emph{lower edge} of LEGEND-1000 sensitivity---detection is plausible but not guaranteed.

\paragraph{nEXO (next-generation Enriched Xenon Observatory).}
nEXO will use 5 tonnes of enriched $^{136}$Xe with projected sensitivity \cite{nEXO:2021ujk}:
\begin{equation}
    \vev{m_{\beta\beta}} > 5.7\text{--}17.7 \text{ meV at } 90\%\text{ CL (nEXO, 2028--2032)}.
\end{equation}
Our prediction $10.5$ meV lies \emph{within the central range} of nEXO sensitivity. If the nuclear matrix elements are near their best-fit values, nEXO should observe a signal at $3$--$5\sigma$ significance by 2030.

\paragraph{Falsification criterion.}
Our prediction is falsifiable via:
\begin{enumerate}
    \item \textbf{Non-observation:} If LEGEND-1000 and nEXO both reach design sensitivity without detecting $0\nu\beta\beta$, implying $\vev{m_{\beta\beta}} < 5$ meV, our framework is \textbf{excluded} at $>3\sigma$ (given our $\pm 1.5$ meV uncertainty).
    
    \item \textbf{Signal at wrong value:} If a signal is detected but $\vev{m_{\beta\beta}} > 20$ meV or $\vev{m_{\beta\beta}} < 5$ meV (outside our $2\sigma$ band), our framework is \textbf{excluded}.
    
    \item \textbf{Confirmation:} If a signal is detected with $\vev{m_{\beta\beta}} = 9$--$12$ meV (our $1\sigma$ band), our framework is \textbf{strongly supported}.
\end{enumerate}

\textbf{Verdict timeline:} 2027--2030 (LEGEND-1000 and nEXO combined).

\subsection{Neutrino CP Violation Phase}

\subsubsection{Theoretical Prediction}

The neutrino CP-violating phase $\delta_{CP}^\nu$ appears in the PMNS matrix (standard parametrization):
\begin{equation}
    U_{\text{PMNS}} = \begin{pmatrix}
        c_{12} c_{13} & s_{12} c_{13} & s_{13} e^{-i\delta_{CP}^\nu} \\
        -s_{12} c_{23} - c_{12} s_{23} s_{13} e^{i\delta_{CP}^\nu} & c_{12} c_{23} - s_{12} s_{23} s_{13} e^{i\delta_{CP}^\nu} & s_{23} c_{13} \\
        s_{12} s_{23} - c_{12} c_{23} s_{13} e^{i\delta_{CP}^\nu} & -c_{12} s_{23} - s_{12} c_{23} s_{13} e^{i\delta_{CP}^\nu} & c_{23} c_{13}
    \end{pmatrix},
\end{equation}
where $c_{ij} = \cos\theta_{ij}$, $s_{ij} = \sin\theta_{ij}$.

From our Yukawa matrix diagonalization (Section~\ref{sec:calculation}), we compute:
\begin{equation}
    \delta_{CP}^\nu = 206^\circ.
    \label{eq:delta_cp_prediction}
\end{equation}

This value arises from the complex phases in the seesaw mechanism, which in turn originate from the modular form $\eta(\tau_*)$ evaluated at the physical vacuum $\tau_* = 2.69i$:
\begin{equation}
    \arg[\eta(\tau_*)] = 0,
\end{equation}
since $\tau_*$ is pure imaginary, making $\eta(\tau_*)$ real-valued. The non-trivial CP phase arises instead from the \emph{texture} of the Yukawa matrices---specifically, the relative phases between different modular forms ($E_4$, $E_6$, $\eta$) and their interplay in the seesaw formula (Eq.~\ref{eq:seesaw}).

\paragraph{Uncertainty estimate.}
The phase uncertainty arises from:
\begin{itemize}
    \item Moduli stabilization ($3.5\%$) translates to $\sim 7^\circ$ phase variation
    \item Higher-order modular form corrections: $\sim 5^\circ$
    \item Charged lepton mixing contributions: $\sim 3^\circ$
\end{itemize}

Combining: $\Delta \delta_{CP}^\nu \approx \sqrt{7^2 + 5^2 + 3^2} \approx 9^\circ$.

Conservative estimate with systematic uncertainties:
\begin{equation}
    \boxed{\delta_{CP}^\nu = (206 \pm 15)^\circ}
    \label{eq:delta_cp_final}
\end{equation}

\subsubsection{Experimental Status and Timeline}

Current measurements of $\delta_{CP}^\nu$ come from long-baseline neutrino oscillation experiments:

\begin{itemize}
    \item \textbf{T2K} (2022): $\delta_{CP}^\nu = 197^{+27}_{-24}$ deg (68\% CL) \cite{T2K:2021xwb}
    \item \textbf{NOvA} (2021): $\delta_{CP}^\nu = 144^{+38}_{-28}$ deg or $278^{+23}_{-28}$ deg (68\% CL) \cite{NOvA:2021nfi}
    \item \textbf{Global fit} (NuFIT 5.2): $\delta_{CP}^\nu = 197^{+27}_{-24}$ deg (68\% CL) \cite{Esteban:2020cvm}
\end{itemize}

The current best-fit $197^\circ$ is consistent with our prediction $206^\circ$ within $0.3\sigma$. However, uncertainties are large ($\pm 25^\circ$), preventing definitive confirmation or exclusion.

\paragraph{DUNE (Deep Underground Neutrino Experiment).}
DUNE is a next-generation long-baseline experiment with 40 kt liquid argon detector at 1,300 km baseline. Projected sensitivity \cite{DUNE:2020fgq}:
\begin{equation}
    \Delta \delta_{CP}^\nu \approx 10^\circ\text{--}15^\circ \quad \text{at } 1\sigma \text{ (DUNE, 2027--2035)}.
\end{equation}

DUNE will measure $\delta_{CP}^\nu$ with precision comparable to our theoretical uncertainty. If DUNE confirms $\delta_{CP}^\nu \approx 200^\circ \pm 10^\circ$, our prediction is validated. If DUNE finds $\delta_{CP}^\nu < 150^\circ$ or $\delta_{CP}^\nu > 250^\circ$ at $3\sigma$, our framework is excluded.

\paragraph{Hyper-Kamiokande.}
Hyper-K (2027+) will provide complementary measurements with similar precision \cite{Hyper-Kamiokande:2018ofw}. Combined DUNE + Hyper-K analysis will achieve $\Delta \delta_{CP}^\nu \sim 5^\circ$ by 2035.

\textbf{Falsification criterion:}
\begin{itemize}
    \item \textbf{Exclusion:} $\delta_{CP}^\nu < 175^\circ$ or $\delta_{CP}^\nu > 240^\circ$ at $>3\sigma$ by DUNE/Hyper-K.
    \item \textbf{Confirmation:} $\delta_{CP}^\nu = 190^\circ$--$220^\circ$ at $2\sigma$ by 2030.
\end{itemize}

\textbf{Verdict timeline:} 2027--2032 (DUNE first results), 2035 (DUNE + Hyper-K combined).

\subsection{Sum of Neutrino Masses from Cosmology}

\subsubsection{Theoretical Prediction}

Our framework predicts absolute neutrino masses:
\begin{equation}
    m_1 = 1.2 \text{ meV}, \quad m_2 = 8.7 \text{ meV}, \quad m_3 = 50.1 \text{ meV}.
\end{equation}

The sum of neutrino masses affects cosmic microwave background (CMB) anisotropies and large-scale structure formation:
\begin{equation}
    \Sigma m_\nu = m_1 + m_2 + m_3 = 60.0 \text{ meV}.
    \label{eq:sum_masses_prediction}
\end{equation}

Neutrinos become non-relativistic when their momenta drop below their masses, affecting the matter-radiation transition and suppressing structure growth below the free-streaming scale. The CMB acoustic peaks and matter power spectrum are sensitive to $\Sigma m_\nu$ at the level of $\sim 10$ meV.

\paragraph{Uncertainty estimate.}
The $3.5\%$ moduli stabilization systematic propagates to:
\begin{equation}
    \Delta(\Sigma m_\nu) \approx 0.035 \times 60 \text{ meV} \approx 2 \text{ meV}.
\end{equation}

Including neutrino mass splitting uncertainties ($\Delta m_{21}^2$ and $\Delta m_{31}^2$ measured to $\sim 3\%$ precision):
\begin{equation}
    \boxed{\Sigma m_\nu = (60 \pm 8) \text{ meV}}
    \label{eq:sum_masses_final}
\end{equation}

The larger uncertainty ($\pm 8$ meV) reflects that absolute mass scale depends sensitively on the lightest neutrino mass $m_1$, which is not directly measured by oscillations.

\subsubsection{Experimental Status and Timeline}

Current cosmological constraints from Planck + BAO + weak lensing \cite{Planck:2018vyg}:
\begin{equation}
    \Sigma m_\nu < 120 \text{ meV (95\% CL, Planck 2018)}.
\end{equation}

Our prediction $60 \pm 8$ meV is well below this limit but will be tested by next-generation surveys:

\paragraph{CMB-S4 (CMB Stage-4).}
CMB-S4 is a next-generation ground-based CMB experiment with $\sim 500{,}000$ detectors. Projected sensitivity \cite{CMB-S4:2016ple}:
\begin{equation}
    \Sigma m_\nu > 15 \text{ meV at } 2\sigma \text{ (CMB-S4 + DESI, 2028--2032)}.
\end{equation}

If $\Sigma m_\nu = 60$ meV, CMB-S4 will detect the signature at $\gtrsim 5\sigma$ significance. This would be the first direct cosmological detection of the absolute neutrino mass scale.

\paragraph{Euclid and LSST.}
Euclid space mission (2024--2030) and Vera C. Rubin Observatory LSST (2025--2035) will measure weak gravitational lensing and galaxy clustering with unprecedented precision. Combined with CMB-S4, projected sensitivity:
\begin{equation}
    \Delta(\Sigma m_\nu) \approx 10\text{--}15 \text{ meV (CMB-S4 + Euclid + LSST, 2030--2035)}.
\end{equation}

This precision is sufficient to confirm or exclude our prediction $\Sigma m_\nu = 60 \pm 8$ meV at $3\sigma$.

\textbf{Falsification criterion:}
\begin{itemize}
    \item \textbf{Exclusion:} $\Sigma m_\nu < 40$ meV or $\Sigma m_\nu > 85$ meV at $>3\sigma$ by CMB-S4 + surveys.
    \item \textbf{Confirmation:} $\Sigma m_\nu = 50$--$70$ meV at $2\sigma$ by 2032.
\end{itemize}

\textbf{Verdict timeline:} 2028--2032 (CMB-S4 first results), 2035 (full combination).

\subsection{Summary: Three Independent Tests by 2030}

Table~\ref{tab:predictions_summary} summarizes our falsifiable predictions:

\begin{table}[h!]
\centering
\caption{Testable predictions with experimental timeline. All three predictions are outputs of the topological framework, not fitted parameters.}
\label{tab:predictions_summary}
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Observable} & \textbf{Prediction} & \textbf{Current Status} & \textbf{Experiment} & \textbf{Timeline} \\ \midrule
$\vev{m_{\beta\beta}}$ & $(10.5 \pm 1.5)$ meV & $< 36$--$156$ meV & LEGEND/nEXO & 2027--2030 \\
$\delta_{CP}^\nu$ & $(206 \pm 15)^\circ$ & $197^{+27}_{-24}$ deg & DUNE/Hyper-K & 2027--2032 \\
$\Sigma m_\nu$ & $(60 \pm 8)$ meV & $< 120$ meV & CMB-S4/Euclid & 2028--2032 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Correlation between predictions.}
These three observables are \emph{not independent} but related through neutrino mass eigenvalues and PMNS matrix. If one is confirmed, the others become more likely. Conversely, if one is excluded, the entire framework is called into question. This provides a \emph{self-consistency check}:

\begin{itemize}
    \item If $\vev{m_{\beta\beta}} = 10.5$ meV is confirmed by nEXO, then $\Sigma m_\nu \approx 60$ meV is essentially guaranteed (given $m_3 \approx 50$ meV required to match $\Delta m_{31}^2$).
    
    \item If $\delta_{CP}^\nu \approx 206^\circ$ is confirmed by DUNE, it constrains the complex phases in the seesaw, making $\vev{m_{\beta\beta}}$ more predictive.
    
    \item If CMB-S4 finds $\Sigma m_\nu < 40$ meV, it implies $m_3 < 40$ meV, contradicting neutrino oscillation data ($\Delta m_{31}^2 = 2.5 \times 10^{-3}$ eV$^2$ requires $m_3 \gtrsim 50$ meV for $m_1 \ll m_2$). This would exclude our framework.
\end{itemize}

\subsection{Falsifiability: How to Kill This Theory}

We explicitly state what would falsify our framework:

\paragraph{Definitive falsification (>5$\sigma$):}
\begin{enumerate}
    \item \textbf{LEGEND-1000 and nEXO reach design sensitivity without detecting $0\nu\beta\beta$,} implying $\vev{m_{\beta\beta}} < 5$ meV. This would exclude our prediction $10.5 \pm 1.5$ meV at $>3\sigma$.
    
    \item \textbf{DUNE measures $\delta_{CP}^\nu < 150^\circ$ or $> 250^\circ$ at $>3\sigma$.} This would be inconsistent with our prediction $206 \pm 15^\circ$.
    
    \item \textbf{CMB-S4 + surveys constrain $\Sigma m_\nu < 35$ meV at $>3\sigma$.} This would contradict both our prediction and oscillation data (tension with $\Delta m_{31}^2$).
    
    \item \textbf{Inverted mass ordering definitively established.} Our framework assumes normal ordering. If future oscillation experiments (JUNO, Hyper-K) establish inverted ordering at $>5\sigma$, our neutrino sector predictions are excluded.
\end{enumerate}

\paragraph{Strong tension (3--5$\sigma$):}
\begin{enumerate}
    \item Discovery of $0\nu\beta\beta$ with $\vev{m_{\beta\beta}} > 20$ meV or $< 5$ meV.
    \item DUNE measures $\delta_{CP}^\nu = 150^\circ \pm 10^\circ$ (CP-conserving or near-maximal CP violation).
    \item Future measurements of CKM matrix element $|V_{cd}|$ confirm current tension at $>3\sigma$ (our prediction $0.2252$ vs PDG $0.221 \pm 0.004$).
\end{enumerate}

\paragraph{What would \emph{not} falsify the framework:}
\begin{itemize}
    \item Small ($1$--$2\sigma$) deviations in quark masses or mixing angles. These could be accommodated by moduli variations within KKLT bounds.
    \item Non-detection of $0\nu\beta\beta$ at sensitivity $\sim 15$ meV (current experiments). This is consistent with our prediction $10.5$ meV.
    \item Modest changes to PDG central values within current uncertainties. Our framework is designed to be robust to $\sim 5\%$ variations.
\end{itemize}

\subsection{Implications of Confirmation}

If all three predictions are confirmed by 2030--2035:

\begin{enumerate}
    \item \textbf{String theory produces falsifiable physics.} This would demonstrate that string landscape constructions can yield concrete, testable predictions on human timescales, countering criticisms of unfalsifiability.
    
    \item \textbf{Flavor structure has geometric origin.} Confirmation would support the hypothesis that SM flavor parameters encode information about extra-dimensional topology, not anthropic selection or environmental randomness.
    
    \item \textbf{Modular flavor symmetries are physical.} The success of modular forms in reproducing hierarchies would validate their role as fundamental symmetries arising from string compactification geometry.
    
    \item \textbf{Neutrinos are Majorana particles.} Detection of $0\nu\beta\beta$ would establish neutrino Majorana nature and lepton number violation, with implications for leptogenesis and baryogenesis.
    
    \item \textbf{Systematic landscape exploration becomes viable.} Our proof-of-principle would motivate systematic scans of the string landscape for other phenomenologically viable configurations, potentially uncovering patterns or selection principles.
\end{enumerate}

\subsection{Timeline for Verdict}

\begin{figure}[h!]
\centering
\begin{tikzpicture}[scale=1.2]
    % Timeline axis
    \draw[thick,->] (0,0) -- (11,0) node[right] {Year};
    
    % Year markers
    \foreach \x/\year in {0/2024, 2/2026, 4/2028, 6/2030, 8/2032, 10/2034} {
        \draw (\x,0.1) -- (\x,-0.1) node[below] {\year};
    }
    
    % Experiment bars
    \draw[thick,blue,fill=blue!20] (2,1) rectangle (6,1.5) node[midway] {\small LEGEND-1000};
    \draw[thick,red,fill=red!20] (3,2) rectangle (8,2.5) node[midway] {\small nEXO};
    \draw[thick,green!50!black,fill=green!20] (2,3) rectangle (8,3.5) node[midway] {\small DUNE};
    \draw[thick,orange,fill=orange!20] (3,4) rectangle (8,4.5) node[midway] {\small CMB-S4};
    
    % Verdict markers
    \node[circle,fill=blue,inner sep=2pt] at (6,1.25) {};
    \node[circle,fill=red,inner sep=2pt] at (8,2.25) {};
    \node[circle,fill=green!50!black,inner sep=2pt] at (8,3.25) {};
    \node[circle,fill=orange,inner sep=2pt] at (8,4.25) {};
    
    % Labels
    \node[right] at (6.2,1.25) {\tiny $\vev{m_{\beta\beta}}$ (2030)};
    \node[right] at (8.2,2.25) {\tiny $\vev{m_{\beta\beta}}$ (2032)};
    \node[right] at (8.2,3.25) {\tiny $\delta_{CP}^\nu$ (2032)};
    \node[right] at (8.2,4.25) {\tiny $\Sigma m_\nu$ (2032)};
    
    % Today marker
    \draw[thick,dashed] (0.5,0) -- (0.5,5) node[above] {\textbf{Today}};
    
    % Verdict window
    \draw[thick,purple,fill=purple!10,opacity=0.3] (5.5,0) rectangle (8.5,5);
    \node[purple,font=\bfseries] at (7,4.8) {VERDICT};
    \node[purple] at (7,0.5) {2030--2032};
\end{tikzpicture}
\caption{Experimental timeline for testing our predictions. All three tests converge on the 2030--2032 window. Purple band indicates when a definitive verdict (confirmation or exclusion) is expected.}
\label{fig:timeline}
\end{figure}

\textbf{Bottom line:} By 2032, this framework will be either \emph{confirmed as a viable string-theoretic origin of flavor} or \emph{definitively excluded} by experimental data. There is no ambiguity, no moving goalposts, no retrofitting. The theory lives or dies on these three predictions.

This is \emph{falsifiable physics}.
